% Stephen Montgomery-Smith's Reduced C.V.
% LaTeX

\documentclass{article}

\setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0in}

\newcommand{\littlesection}[1]{\section*{\normalsize\bf #1}}

\begin{document}

\title{Publications}
\author{Stephen Montgomery-Smith}
\maketitle

\littlesection{Books Edited}

\begin{enumerate}
\item (with N.~Kalton and E.~Saab), Interaction Between Functional
Analysis, Harmonic Analysis, and Probability, Proceedings of Conference
held in Columbia, Missouri on May 1994, Lecture Notes in Pure and
Appl.\ Math., 175, Marcel Dekker, New York, 1995.
\end{enumerate}

\littlesection{Unrefereed Publications}

\begin{enumerate}
\item Orlicz--Lorentz Spaces, {\em Proceedings of the Orlicz
Memorial Conference}, (Ed.\ P.~Kranz and I.~Labuda), Oxford, Mississippi
(1991).
\end{enumerate}

\littlesection{Refereed Publications}

\begin{enumerate}
\item (with R.~Ober) Bilinear transformation of infinite dimensional state
space systems
and balanced realizations of nonrational transfer functions, {\em 
S.I.A.M.\ J.\ of Control {\bf 28} (1990), 438--465}.
\item The Gaussian cotype of operators from $C(K)$, {\em Israel
Journal of Math.\ {\bf 68} (1989), 123--128}.
\item The distribution of Rademacher sums, {\em 
Proc.\ A.M.S.\ {\bf 109}
(1990), 517--522}.
\item The $p^{1\over p}$\ in Pisier's factorization
theorem, {\em 
Proceedings of Conference on Geometry of Spaces at Strobl, Ed.: 
P.F.X.~M\"uller and W.~Schachermayer, L.M.S.\ 1990}.
\item (with M.~Talagrand) The Rademacher cotype of operators from
$l_\infty^N$, {\em Proc.\ A.M.S.\ {\bf 112} (1991), 187--194}.
\item (with D.J.H.~Garling) Complemented subspaces of spaces
obtained by interpolation, {\em J.\ L.M.S.\ (2) {\bf 44} (1991), 
503--513}.
\item (with P.~Saab) $p$-summing operators on injective tensor
products of spaces, {\em B.\ Royal Soc.\ Edin.\ {\bf 120A}, (1992), 
283--296}.
\item Comparison of Orlicz--Lorentz spaces, {\em 
Stud.\ Math.\ {\bf 103 (2)}, (1992), 161--189}.
\item (with N.~Asmar) On the distribution of 
Sidon series, {\em Arkiv Mat.\ {\bf 31}, (1993), 13--26}.
\item (with S.J.~Dilworth)
The distribution of vector-valued Rademacher series, {\em Annals Prob.\
{\bf 21}, (1993), 2046--2052}.
\item (with N.~Asmar) Littlewood--Payley Theory on solenoids, {\em
Colloq.\ Math.\ {\bf 65}, (1993), 69--82}.
\item (with N.J.~Kalton) Set functions and factorization, {\em
Arch.\ Math.\ {\bf 61}, (1993), 183--200}.
\item The distribution of non-commutative Rademacher series, {\em
Math.\ Ann.\ {\bf 302}, (1995), 395--416}.
\item (with V.H.~de~la~Pe\~na and J.~Szulga) 
Contraction and decoupling inequalities for  
multilinear forms and U-statistics, {\em
Annals Prob., {\bf 22}, (1994), 1745--1765}.
\item (with Y.~Latushkin) Lyapunov Theorems for Banach Spaces, {\em
Bul.\ A.M.S.\ {\bf 31}, (1994), 44--49}.
\item (with Y.~Latushkin) Evolutionary semigroups and Lyapunov theorems
in Banach spaces, {\em J.\ Func.\ Anal.\ {\bf 127}, (1995), 173--197}.
\item (with V.H.~de~la~Pe\~na) Bounds on the Tail Probability of 
U-Statistics and Quadratic Forms, {\em Bul.\ A.M.S.\ {\bf 31}, (1994),
223--227}.
\item Comparison of sums of independent identically distributed 
random vectors, {\em Prob.\ and Math.\ Stat.\ {\bf 14}, (1993), 
281--285}.
\item (with V.H.~de~la~Pe\~na) Decoupling Inequalities for the 
Tail Probabilities of
Multivariate U-statistics, {\em Annals Prob.\ {\bf 23}, (1995), 806--816}.
\item (with P.~Hitzcenko)
Tangent Sequences in Orlicz and Rearrangement Invariant
Spaces, {\em Proc.\ Camb.\ Phil.\ Soc.\ {\bf 119}, (1996),
91--101.}
\item The Hardy operator and Boyd indices, 
{\em 
Interaction between Probability, Harmonic Analysis and Functional Analysis,
Ed.: N.~Kalton, S.J.~Montgomery-Smith, E.~Saab, 
Lecture Notes in Pure and
Appl.\ Math., 175, Marcel Dekker, New York, 1995.}
\item Boyd Indices of Orlicz--Lorentz spaces, {\em
Function Spaces, The Second Conference, Ed.: K.~Jarosz,
321--334, Marcel Dekker, 1995.}
\item (with C.~Chicone and Y.~Latushkin)
The spectrum of the kinematic dynamo operator for an ideally conducting
fluid, {\em Commun.\ Math.\ Phys.\ {\bf 173}, (1995), 379--400.}
\item (with Y.~Latushkin and T.~Randolph) 
Evolutionary semigroups and dichotomy of linear skew-product flows
on locally compact spaces with Banach fibers, {\em 
J.\ Diff.\ Eq.\ {\bf 125}, (1996), 73--116.}
\item Stability and dichotomy of positive semigroups on $L_p$, {\em
Proc.\ A.M.S.\ {\bf 8}, (1996), 2433--2437.}
\item (with A.L.~Koldobsky)
Inequalities of correlation type for symmetric stable 
random vectors, {\em Stat.\ \& Prob.\ Letters.\ {\bf 28}, (1996), 91--97.}
\item (with N.~Asmar and B.~Kelly)
A note on UMD spaces and transference in vector-valued
function spaces, {\em Proc.\ Edin.\ Math.\ Soc.\ {\bf 39}, (1996),
485--490}.
\item (with N.~Asmar) Hahn's Embedding Theorem on orders and harmonic
analysis on groups with ordered duals, {\em Colloq.\ Math.\ {\bf 70},
(1996), 235--252.}
\item (with C.~Chicone and Y.~Latushkin) The Annular Hull Theorems for the 
Kinematic Dynamo Operator for an Ideally Conducting Fluid, {\em
Indiana J.\ {\bf 45}, (1996), 361--379.}
\item (with L.~Grafakos) Best constants for uncentered maximal functions, 
{\em 
Bul.\ L.M.S.\ {\bf 29}, (1997), 60--64.}
\item (with P.~Hitczenko and K.~Oleszkiewicz) Moment inequalities for linear
combinations of certain independent random variables, {\em
Studia Math.\ {\bf 123}, (1997), 15--42.}
\item (with N.~Asmar) Hardy martingales and Jensen's Inequality, {\em
Bull.\ Australian Math.\ Soc.\ {\bf 55}, (1997), 185--195.}
\item (with N.~Asmar)
On a weak type $(1,1)$ inequality for a maximal conjugate
function, {\em Studia Math.\ {\bf 125}, (1997),
13--21.}
\item Time decay for the bounded mean oscillation of solutions of
the Schr\"odinger and wave equations, {\em Duke Math.\
J.\ {\bf 91}, (1998), 393--408.}
\item (with N.~Asmar)
Analytic measures and Bochner measurability, {\em
Bull.\ Sc.\ Math.\ {\bf 122}, (1998), 39--66.}
\item (with N.~Asmar) A transference theorem for ergodic $H^1$,
{\em Quarterly J.\ of Math.\ {\bf 48}, (1997), 417--430.}
\item (with N.~Asmar and A.~Kelly) Vector-valued weakly analytic measures,
{\em Hokkaido Math.\ J., {\bf 27}, (1998), 457--473.}
\item (with E.~Semenov) Random rearrangmements and operators, {\em
25 Years of Voronezh Winter Mathematical School, Proceedings in
honor of 80th birthday of S.~Krein, A.M.S.}
\item Concrete representation of martingales,
{\em Electronic J. Probab.\ {\bf 3}, (1998), paper 15.}
\item Global regularity of the Navier-Stokes equation on thin
three dimensional domains with periodic boundary conditions,
{\em Electronic J.\ of Differential Equations {\bf 1999}, (1999), no.\ 11,
1--19.}
\item (with L.~Grafakos and O.~Motrunich) A sharp estimate for the
Hardy-Littlewood maximal function, {\em
Studia Math.\ {\bf 134}, (1999), 57--67.}
\item (with P.~Hitczenko) A note on sums of independent random variables,
{\em Advances in Stochastic Inequalities, Ed.: T.~Hill and C.~Houdr\'e,
Contemporary Mathematics 234, A.M.S., Providence R.I., 1999.}
\item (with N.~Asmar and S.~Saeki) Transference in spaces of measures,
{\em J.\ Functional Analysis {\bf 165}, (1999), 1--23.}
\item (with E.~Semenov) Title in Russian --- translation:
Averaging of Fourier-Haar coefficients,
{\em Math.\ Sbornik.\ {\bf 190}, (1999), 49--64.}
\item (with A.~Baernstein) Some conjectures about integral means
of $\partial f$ and $\bar\partial f$,
{\em Complex Analysis and Differential Equations, edited by C.Kiselman, Acta
Universitatis Upsaliensis C., Volume 64 (1999), 92--109.}
\item (with S.~Clark, Y.~Latushkin and T.~Randolph)
Stability radius and internal versus external stability in Banach spaces:
an evolution semigroup approach, {\em S.I.A.M.\ J.\ of
Control Optim. {\bf 38}, (2000), 1757--1793.}
\item (with E.~Semenov) Embeddings of rearrangement invariant spaces
that are not strictly singular, {\em Positivity {\bf 4}, (2000), 397--402.}
\item (with A.~Pruss) A comparison inequality for sums of independent
random variables, {\em J.M.A.A. {\bf 254}, (2001), 35--42.}
\item (with P.~Hitczenko) Measuring the magnitude of sums of independent
random variables, {\em Annals Probability {\bf 29}, (2001), 447--466.}
\item Finite time blow up for a Navier-Stokes like equation,
{\em Proc.\ A.M.S., {\bf 129}, (2001), 3017--3023.}
\item (with N.~Asmar) Decomposition of analytic measures on groups,
{\em Studia Math, {\bf 146}, (2001), 261--284.}
\item (with M.~Pokorn\'y) A counterexample to the smoothness of the solution
to an equation arising in fluid mechanics, {\em
Commentationes Mathematicae Universitatis Carolinae, {\bf 43, 1}, (2002),
61--75.}
\item Rearrangement Invariant Norms of Symmetric Sequence Norms of
Independent Sequences of Random Variables, {\em Israel Journal
of Mathematics, {\bf 131}, (2002), 51--60.}
\end{enumerate}

%\littlesection{Papers Accepted for Publication}

%\begin{enumerate}
%\end{enumerate}

\end{document}

